Moral Foundations of U.S. Political News Organizations

### 2018-12-04 pilot_manuscript.Rmd
update and comments
updated the reference

##Moral Foundations Theory

@@

The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@GILLIGAN1991]. *LET'S CHECK THIS CITATION IN MENDELEY*!.The first two foundations (*harm/care* and *fairness/reciprocity*) are termed the "individualizing foundations," as they are centered on the concerns of individuals rather than groups. *Harm/care* represents an endorsement of compassion and kindness, while opposing cruelty and harm. *Fairness/reciprocity* represents concerns centered on guaranteeing individual rights as well as justice and equality among all people. The other three foundations (*ingroup/loyalty*, *authority/respct*, and *purity/sanctity*) are the "binding" foundations, owing to their focus on group-related concerns, rather than those of individuals. *Ingroup/loyalty* represents endorsements of patriotism and heroism and discourages nonconformity and dissent. *Authority/respect* represents an endorsement of social hierarchies and traditions while denigrating disobedience. Finally, *purity/sanctity* represents concerns regarding chastity and piety, while discouraging vices and indulgences, including lust, avarice, and gluttony [@Haidt2007]. Liberals tend to endorse the individualizing foundations more than conservatives. Endorsements for the three binding foundations, however, are lower than conservatives. Conservatives, on the other hand, tend to endorse all five foundations equally, implying they base judments (at least partially) on each foundation [@Graham2009].

##Moral Foundations Dictionary

@@

##Valence

@@

##Kavanaugh Supreme Court Hearing

>>>>

## Moral Foundations Theory

@@

The researchers settled on these specific foundations after the completion of a literature survey of research in anthropology and evolutionary psychology [@Graham2011].The first two foundations (*harm/care* and *fairness/reciprocity*) are termed the "individualizing foundations," as they are centered on the concerns of individuals rather than groups. *Harm/care* represents an endorsement of compassion and kindness, while opposing cruelty and harm. *Fairness/reciprocity* represents concerns centered on guaranteeing individual rights as well as justice and equality among all people. The other three foundations (*ingroup/loyalty*, *authority/respct*, and *purity/sanctity*) are the "binding" foundations, owing to their focus on group-related concerns, rather than those of individuals. *Ingroup/loyalty* represents endorsements of patriotism and heroism and discourages nonconformity and dissent. *Authority/respect* represents an endorsement of social hierarchies and traditions while denigrating disobedience. Finally, *purity/sanctity* represents concerns regarding chastity and piety, while discouraging vices and indulgences, including lust, avarice, and gluttony [@Haidt2007]. Liberals tend to endorse the individualizing foundations more than conservatives. Endorsements for the three binding foundations, however, are lower than conservatives. Conservatives, on the other hand, tend to endorse all five foundations equally, implying they base judments (at least partially) on each foundation [@Graham2009].

## Moral Foundations Dictionary

@@

## Valence

@@

## Kavanaugh Supreme Court Hearing
